---
title: "Text Analysis and Novels"
---

```{r, echo=FALSE}
options(warn = -1)
library(NLP)
library(RColorBrewer)
library(tm)
library(ggplot2)
library(topicmodels)
library(skmeans)
library(clue)
library(fpc)
library(cluster)
library(wordcloud)
library(stringdist)
library(slam)
library(wordcloud)
library(textstem)
library(grid)
library(gtable)
library(tidytext)
library(dplyr)
library(tidyr)
library(plotly)
library(udpipe)
library(igraph)
library(SnowballC)
library(textstem)

```

Downloading Novels 'The Awakening' and 'The Aspern Papers'
```{r}
awakening <- scan("http://www.gutenberg.org/files/160/160-0.txt", what="character", blank.lines.skip = TRUE, sep="\n")
aspern <- scan("http://www.gutenberg.org/files/211/211-0.txt", what="character", blank.lines.skip = TRUE, sep="\n")

awakening<- iconv(awakening, 'utf-8', 'ascii', sub='')
aspern<- iconv(aspern, 'utf-8', 'ascii', sub='')
```


Cleaning the novels
```{r}
awakening.begin <- which(awakening=="THE AWAKENING")[2]
awakening.end   <- which(awakening=="*****") - 1
awakening.v<- awakening[awakening.begin:awakening.end]
head(awakening.v)
tail(awakening.v)


aspern.begin <- which(aspern=="Macmillan and Co., 1888.")+1
aspern.end   <- which(aspern=="End of the Project Gutenberg EBook of The Aspern Papers, by Henry James") - 1
aspern.v <- aspern[aspern.begin:aspern.end]
head(aspern.v)
tail(aspern.v)
```

Awakening:

1. Cutting in chapters and corpus creation
```{r}
awakening.v <- gsub("^I*(X|V)*I*$", "@@@", awakening.v)
awakening.string <- paste(awakening.v, collapse = " ")
awakening.chapters <- strsplit(awakening.string, "@@@ ") 
awakening.df <- as.data.frame(awakening.chapters, stringsAsFactors = FALSE)
awakening.df <-awakening.df[2:38,1]
awakening.df <- as.data.frame(awakening.df)
colnames(awakening.df) <- "chapters"    
awakening.docs <- Corpus(VectorSource(awakening.df$chapters))
```

2. Text preprocessing
```{r}
toSpace <- content_transformer(function (x , pattern ) gsub(pattern, " ", x))
awakening.docs <- tm_map(awakening.docs, toSpace, "/")
awakening.docs <- tm_map(awakening.docs, toSpace, "@")
awakening.docs <- tm_map(awakening.docs, toSpace, "\\|")
awakening.docs <- tm_map(awakening.docs, content_transformer(tolower))
awakening.docs <- tm_map(awakening.docs, removeNumbers)
awakening.docs <- tm_map(awakening.docs, removeWords, stopwords("english"))
awakening.docs <- tm_map(awakening.docs, removePunctuation)
awakening.docs <- tm_map(awakening.docs, stripWhitespace)
```

3. WordCloud preparation and wordcloud graph
```{r}
awakening.dtm <- DocumentTermMatrix(awakening.docs, control=list(weighting=weightTf))
awakening.m <- as.matrix(t(awakening.dtm))
awakening_v <- sort(rowSums(awakening.m),decreasing=TRUE)
awakening.d <- data.frame(word = names(awakening_v),freq=awakening_v)
head(awakening.d, 10)
set.seed(1234)
wordcloud(words = awakening.d$word, freq = awakening.d$freq, min.freq = 1,
          max.words=200, random.order=FALSE, rot.per=0.35,
          colors=brewer.pal(8, "Dark2"))
```


Aspern

1. Cutting in chapters and corpus creation
```{r}
aspern.v <- gsub("^I*(X|V)*I*$", "@@@", aspern.v)
aspern.string <- paste(aspern.v, collapse = " ")
aspern.chapters <- strsplit(aspern.string, "@@@ ") 
aspern.df <- as.data.frame(aspern.chapters, stringsAsFactors = FALSE)
aspern.df <-aspern.df[2:38,1]
aspern.df <- as.data.frame(aspern.df)
colnames(aspern.df) <- "chapters"
aspern.docs <- Corpus(VectorSource(aspern.df$chapters))

```


2. Text preprocessing

```{r}
toSpace <- content_transformer(function (x , pattern ) gsub(pattern, " ", x))
aspern.docs <- tm_map(aspern.docs, toSpace, "/")
aspern.docs <- tm_map(aspern.docs, toSpace, "@")
aspern.docs <- tm_map(aspern.docs, toSpace, "\\|")
aspern.docs <- tm_map(aspern.docs, content_transformer(tolower))
aspern.docs <- tm_map(aspern.docs, removeNumbers)
aspern.docs <- tm_map(aspern.docs, removeWords, stopwords("english"))
aspern.docs <- tm_map(aspern.docs, removePunctuation)
aspern.docs <- tm_map(aspern.docs, stripWhitespace)

```

3. WordCloud preparation and wordcloud graph

```{r}
aspern.dtm <- DocumentTermMatrix(aspern.docs, control=list(weighting=weightTf))
aspern.m <- as.matrix(t(aspern.dtm))
aspern_v <- sort(rowSums(aspern.m),decreasing=TRUE)
aspern.d <- data.frame(word = names(aspern_v),freq=aspern_v)
head(aspern.d, 10)
set.seed(1234)
wordcloud(words = aspern.d$word, freq = aspern.d$freq, min.freq = 1,
          max.words=200, random.order=FALSE, rot.per=0.35,
          colors=brewer.pal(8, "Dark2"))

```

Commonality cloud and Comparison cloud

1. Creation of a corpus out of the both texts
```{r}
cc.docs <- Corpus(VectorSource(c(awakening.string,aspern.string)))
```

2. Text preprocessing

```{r}
toSpace <- content_transformer(function (x , pattern ) gsub(pattern, " ", x))
cc.docs <- tm_map(cc.docs, toSpace, "/")
cc.docs <- tm_map(cc.docs, toSpace, "@")
cc.docs <- tm_map(cc.docs, toSpace, "\\|")
cc.docs <- tm_map(cc.docs, content_transformer(tolower))
cc.docs <- tm_map(cc.docs, removeNumbers)
cc.docs <- tm_map(cc.docs, removeWords, stopwords("english"))
cc.docs <- tm_map(cc.docs, removePunctuation)
cc.docs <- tm_map(cc.docs, stripWhitespace)

```

3.Comparison and Commonality cloud

```{r}
cc.dtm <- DocumentTermMatrix(cc.docs)
cc.m <- as.matrix(t(cc.dtm))
colnames(cc.m)<- c("Awakening","Aspern")
comparison.cloud(cc.m,max.words = 100,min.frrandom.order=FALSE)
commonality.cloud(cc.m,max.words = 100,colors = "steelblue1",min.frrandom.order=FALSE)
```


Sentiment timeline
```{r, echo=FALSE}
library(tidytext)
library(dplyr)
library(tidyr)
library(plotly)
library(ggthemes)
library(sentimentr)
library(syuzhet)
data("sentiments")
afinn <- get_sentiments("afinn")
bing <- get_sentiments("bing")
loughran <- get_sentiments("loughran")
nrc <- get_sentiment_dictionary('nrc', language = "english")
```


1.Awakening
```{r}
sent.awakening <- readLines("http://www.gutenberg.org/files/160/160-0.txt")
sent.awakening <-iconv(sent.awakening, 'utf-8', 'ascii', sub='')
awakening.corpus <- VCorpus(VectorSource(sent.awakening))
awakening.corpus <- tm_map(awakening.corpus, content_transformer(tolower))
awakening.corpus <- tm_map(awakening.corpus, removeNumbers)
awakening.corpus <- tm_map(awakening.corpus, removeWords, stopwords("english"))
awakening.corpus <- tm_map(awakening.corpus, removePunctuation)
awakening.corpus <- tm_map(awakening.corpus, stripWhitespace)
awakening.dtm <- DocumentTermMatrix(awakening.corpus)
awakening.tidy <- tidy(awakening.dtm)
awakening.tidy$count <-as.numeric(awakening.tidy$count)
colnames(awakening.tidy)[2]<- 'word'
awakening.tidy$document <- as.numeric(awakening.tidy$document)
nrc.joy <- subset(nrc, nrc$sentiment=="joy")
joy.words <- inner_join(awakening.tidy, nrc.joy)
joy.words <- count(joy.words, word)

bing <- get_sentiments("bing")
awakening.sentiment <- inner_join(awakening.tidy, bing)
awakening.sentiment <- count(awakening.sentiment, sentiment, index=document)
awakening.sentiment <- spread(awakening.sentiment, sentiment, n, fill=0)
awakening.sentiment$polarity <- awakening.sentiment$positive - awakening.sentiment$negative
awakening.sentiment$pos <- ifelse(awakening.sentiment$polarity >=0, "pos", "neg")
ggplot(awakening.sentiment, aes(x=index, y=polarity, fill=pos))+geom_bar(stat="identity", position="identity", width=1)
awakening.smooth <- ggplot(awakening.sentiment, aes(index, polarity))

(p2<-awakening.smooth + stat_smooth())


```

2.Aspern
```{r}
sent.aspern <- readLines("http://www.gutenberg.org/files/211/211-0.txt")
aspern.corpus <- VCorpus(VectorSource(sent.aspern))
aspern.corpus <- tm_map(aspern.corpus, content_transformer(tolower))
aspern.corpus <- tm_map(aspern.corpus, removeNumbers)
aspern.corpus <- tm_map(aspern.corpus, removeWords, stopwords("english"))
aspern.corpus <- tm_map(aspern.corpus, removePunctuation)
aspern.corpus <- tm_map(aspern.corpus, stripWhitespace)
sent.aspern <-iconv(sent.aspern, 'utf-8', 'ascii', sub='')
aspern.dtm <- DocumentTermMatrix(aspern.corpus)
aspern.tidy <- tidy(aspern.dtm)
aspern.tidy$count <-as.numeric(aspern.tidy$count)
colnames(aspern.tidy)[2]<- 'word'
aspern.tidy$document <- as.numeric(aspern.tidy$document)
nrc.joy <- subset(nrc, nrc$sentiment=="joy")
joy.words <- inner_join(aspern.tidy, nrc.joy)
joy.words <- count(joy.words, word)

#bing <- subset(sentiments, sentiments$lexicon=='bing')[,-4]
aspern.sentiment <- inner_join(aspern.tidy, bing)
aspern.sentiment <- count(aspern.sentiment, sentiment, index=document)
aspern.sentiment <- spread(aspern.sentiment, sentiment, n, fill=0)
aspern.sentiment$polarity <- aspern.sentiment$positive - aspern.sentiment$negative
aspern.sentiment$pos <- ifelse(aspern.sentiment$polarity >=0, "pos", "neg")
ggplot(aspern.sentiment, aes(x=index, y=polarity, fill=pos))+geom_bar(stat="identity", position="identity", width=1)
aspern.smooth <- ggplot(aspern.sentiment, aes(index, polarity))

(p3<-aspern.smooth + stat_smooth())
```

3. Merging Aspern and Awakening

```{r}
g2 <- ggplotGrob(p2)
g3 <- ggplotGrob(p3)
g <- rbind(g2, g3, size = "first")
g$widths <- unit.pmax(g2$widths, g3$widths)
grid.newpage()
grid.draw(g)

```


Topic Modelling - Pick up 5 topics and try to make sense of the topics giving a label to them

1.Awakening

```{r}
top.mod.awakening.dtm <- DocumentTermMatrix(awakening.corpus, control = list(weighting=weightTf))
burnin = 1000
iter = 1000
keep = 50
set.seed(510)
top.mod.awakening.n <- nrow(top.mod.awakening.dtm)
top.mod.awakening.dtm <- top.mod.awakening.dtm[row_sums(top.mod.awakening.dtm > 0) > 1,]
top.mod.awakening.lda_basic.model<- LDA(top.mod.awakening.dtm, k = 5L, method = "Gibbs",
                      control = list(burnin = burnin, iter = iter, keep = keep, alpha = 1) )
top.mod.awakening.lda.topics <- as.matrix(topics(top.mod.awakening.lda_basic.model))
#top.mod.awakening.lda.topics
top.mod.awakening.lda.terms <- as.matrix(terms(top.mod.awakening.lda_basic.model, 10))
top.mod.awakening.lda.terms<- iconv(top.mod.awakening.lda.terms, 'utf-8', 'ascii', sub='')
#top.mod.awakening.lda.terms


awakening.top10termsPerTopic <- terms(top.mod.awakening.lda_basic.model, 10)
awakening.top10termsPerTopic <- iconv(top.mod.awakening.lda.terms, 'utf-8', 'ascii', sub='')
#awakening.top10termsPerTopic
colnames(awakening.top10termsPerTopic)<-c("Edna in her house/room"," Work, life and love - Leaving the papers after he/she died","Madame Edna - Mademoiselle Ratignolle - Robert","Emotions - Description of a face ","Mrs.Pontellier - Edna - Robert")
awakening.top10termsPerTopic
awakening.topicNames <- apply(awakening.top10termsPerTopic, 2, paste, collapse=" ")
#awakening.topicNames
```

2. Aspern
```{r}
top.mod.aspern.dtm <- DocumentTermMatrix(aspern.corpus, control = list(weighting=weightTf))
burnin = 1000
iter = 1000
keep = 50
set.seed(510)
top.mod.aspern.n <- nrow(top.mod.aspern.dtm)
top.mod.aspern.dtm <- top.mod.aspern.dtm[row_sums(top.mod.aspern.dtm > 0) > 1,]
top.mod.aspern.lda_basic.model<- LDA(top.mod.aspern.dtm, k = 5L, method = "Gibbs",
                                        control = list(burnin = burnin, iter = iter, keep = keep, alpha = 1) )
top.mod.aspern.lda.topics <- as.matrix(topics(top.mod.aspern.lda_basic.model))
#top.mod.aspern.lda.topics
top.mod.aspern.lda.terms <- as.matrix(terms(top.mod.aspern.lda_basic.model, 10))
top.mod.aspern.lda.terms<- iconv(top.mod.aspern.lda.terms, 'utf-8', 'ascii', sub='')
#top.mod.aspern.lda.terms

aspern.top10termsPerTopic <- terms(top.mod.aspern.lda_basic.model, 10)
aspern.top10termsPerTopic <- iconv(top.mod.aspern.lda.terms, 'utf-8', 'ascii', sub='')
#aspern.top10termsPerTopic
colnames(aspern.top10termsPerTopic)<-c("Home - Seeing somebody - description of eyes - leaving","Jeffrey","Tita","Aunt","Time - Woman - Venice")
aspern.top10termsPerTopic
#aspern.topicNames <- apply(aspern.top10termsPerTopic, 2, paste, collapse=" ")
#aspern.topicNames

```


Extract verbs
```{r,message=FALSE,error=FALSE,warning=FALSE}
library(udpipe)
library(igraph)
library(SnowballC)
library(textstem)
model <- udpipe_download_model(language = "english")
udmodel_english <- udpipe_load_model(file = 'data/english-ewt-ud-2.3-181115.udpipe')
```

1.Awakening

```{r,error=FALSE,warning=FALSE,message=FALSE}
awakening.corpus <- VCorpus(VectorSource(sent.awakening))
awakening.corpus <- tm_map(awakening.corpus, content_transformer(tolower))
awakening.corpus <- tm_map(awakening.corpus, removeNumbers)
awakening.corpus <- tm_map(awakening.corpus, removeWords, stopwords("english"))
awakening.corpus <- tm_map(awakening.corpus, removePunctuation)
awakening.corpus <- tm_map(awakening.corpus, stripWhitespace)
awakening.corpus <- tm_map(awakening.corpus, lemmatize_strings)
awakening.corpus <-SnowballC::wordStem(awakening.corpus, language = 'en')
awakening.verbs.s <- udpipe_annotate(udmodel_english, awakening.corpus)
awakening.verbs.x <- data.frame(awakening.verbs.s)
library(lattice)
awakening.stats <- subset(awakening.verbs.x, upos %in% c("VERB")) 
awakening.stats <- txt_freq(awakening.stats$token)
awakening.stats$key <- factor(awakening.stats$key, levels = rev(awakening.stats$key))
awakening.verbs.barchart<- barchart(key ~ freq, data = head(awakening.stats, 20), col = "gold", 
         main = "Most occurring Verbs - Awakening", xlab = "Freq")
awakening.verbs.barchart
```

2. Aspern

```{r}
aspern.corpus <- VCorpus(VectorSource(sent.aspern))
aspern.corpus <- tm_map(aspern.corpus, content_transformer(tolower))
aspern.corpus <- tm_map(aspern.corpus, removeNumbers)
aspern.corpus <- tm_map(aspern.corpus, lemmatize_strings)
aspern.corpus <- tm_map(aspern.corpus, removeWords, stopwords("english"))
aspern.corpus <- tm_map(aspern.corpus, removePunctuation)
aspern.corpus <- tm_map(aspern.corpus, stripWhitespace)
aspern.corpus <-SnowballC::wordStem(aspern.corpus, language = 'en')
aspern.verbs.s <- udpipe_annotate(udmodel_english, aspern.corpus)
aspern.verbs.x <- data.frame(aspern.verbs.s)
library(lattice)
aspern.stats <- subset(aspern.verbs.x, upos %in% c("VERB")) 
aspern.stats <- txt_freq(aspern.stats$token)
aspern.stats$key <- factor(aspern.stats$key, levels = rev(aspern.stats$key))
aspern.verbs.barchart <- barchart(key ~ freq, data = head(aspern.stats, 20), col = "gold", 
         main = "Most occurring Verbs - Aspern", xlab = "Freq")
aspern.verbs.barchart
```

Main points of interpretation:

1. The most common words are names of characters (Edna, Tita...)
2. According to the sentiment analysis, Awakening novel is slightly from the beginning to the end. On the other hand, Aspern has a slight drop in the negative  sentiment, but the end is positive.
3.Awakening is a longer text than Aspern
4.Due to lemmatization could not address the time of speaking (wheater it is told in past or future)
5. Words "said",little","think","house","good","like","one","come","back","thought" are the most common.
